An eight-year-long low-frequency earthquake catalog for Southern Cascadia

### 2022-01-28 paper/answer_reviewers.tex

\bigskip

\textit{Line 312: "We also computed what would be the expected number of LFEs occurring if the tidal stress changes have no influence on LFE activity." It's not clear to me why this (the black lines in Figure 10) varies so dramatically between families, could you explain a bit further?}

\bigskip

%We divided possible values of the Coulomb stress changes into bins and computed the number of hours for which the Coulomb stress change takes values in each bin. As Coulomb stress change often takes small values and rarely takes high values, the expected number of LFEs is higher around 0 and smaller for big negative or positive values. We did not normalize the results, so the expected number of LFEs is proportional to the total number of LFEs occurring for each family. \\

The shape of the black curves are pretty similar for most of the LFE families.  The y-axis scale refers to the histograms and not the theoretical stress so theoretical stress for families D, C4, F, and G1 are pretty similar.  Family A has smaller theoretical stress levels (x axis) and a different shape.  Family B2 is in a transition between A and the other families. These differences may be due to changing slab geometry in the south (Figure 1).

### 2022-01-28 paper/agujournaltemplate_highlighted.tex
Incorporate KC comments

In northern Cascadia, it has been observed that there is an increase in activity downdip of the plate boundary compared to up dip, both for tremor ~\cite{WEC_2011} and LFEs ~\cite{SWE_2019}. We want to verify whether we can see an increase of LFE activity for the downdip LFE families compared to the updip LFE families. Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distant from each other. We first look at three families aligned at latitude about 40.4N (group B, triangles in Figure 1) and show the number of LFEs per day in the left column of Figure 8. We then look at five families aligned at latitude about 40.7N (group C, diamonds in Figure 1) and show the number of LFEs per day in the middle column of Figure 8. Finally, we look at five families aligned at latitude about 41.05N (group G, pentagons in Figure 1) and show the number of LFEs per day in the right column of Figure 8. For all three sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}. It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different for each family, and may have a strong influence on the number of LFEs detected. To summarize the findings, we plot in Figure 9 the \textbf{average time between} LFE events as a function of the distance in the eastern direction from the \textbf{western} limit of the tremor. \textbf{We defined an LFE event as at least five LFEs recorded during a given day. If two events are separated by less than five days, we assume that this is a single event.} We clearly see that the \textbf{average time between} decreases with the down dip distance. The southernmost family A is also added in Figure 9, but does not fit the general trend.\\

>>>>

In northern Cascadia, it has been observed that there is an increase in activity downdip of the plate boundary compared to up dip, both for tremor ~\cite{WEC_2011} and LFEs ~\cite{SWE_2019}. We want to verify whether we can see an increase of LFE activity for the downdip LFE families compared to the updip LFE families. Most families in the northern and central part of the study area are well aligned along the strike direction, however families in the southern part of the subduction zone are more distant from each other. We first look at three families aligned at latitude about 40.4N (group B, triangles in Figure 1) and show the number of LFEs per day in the left column of Figure 8. We then look at five families aligned at latitude about 40.7N (group C, diamonds in Figure 1) and show the number of LFEs per day in the middle column of Figure 8. Finally, we look at five families aligned at latitude about 41.05N (group G, pentagons in Figure 1) and show the number of LFEs per day in the right column of Figure 8. For all three sets of families, LFE events are more frequent for the easternmost family than for the westernmost family, as was also the case in northern Cascadia ~\cite{SWE_2019}. It is more difficult to compare event size and swarm duration as the number of stations and the quality of the templates are different for each family, and may have a strong influence on the number of LFEs detected. To summarize the findings, we plot in Figure 9 the \textbf{average time between} LFE events as a function of the distance in the eastern direction from the \textbf{western} limit of the tremor. \textbf{We assume that there is an LFE event avery time that at least five LFEs are recorded during a given day. If two events are separated by less than five days, we assume that this is a single event.} We clearly see that the \textbf{average time between LFE events} decreases with the down dip distance. The southernmost family A is also added in Figure 9, but does not fit the general trend.\\
